Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Fixed using 'mode' attribute for 'cull' node instead of 'faces'

\begin{Verbatim}[fontsize=\small]
  <cull mode="back" />
  <framebuffer>
    <attachment usage="color" link="coords-texture-1" />
    <use program="primary-coords-program">
      <uniform name="MVPMatrix" usage="modelviewprojection" />
      <instance of="cube-1-group" />
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="fourth-pass-program">
      <instance of="intersection-group" />
    </use>
  </framebuffer>
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <blend enabled="true" />
  <depth function="less" />
  <sort>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-1" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-1-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull faces="back" />
        <group id="cube-1-group">
          <translate x="-1">
            <cube id="cube-1" />
          </translate>
        </group>
      </use>
    </group>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-2" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-2-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull mode="back" />
        <group id="cube-2-group">
          <translate x="+1">
            <cube id="cube-2" />
          </translate>
        </group>
      </use>
    </group>
  </sort>
\end{Verbatim}

>>>>

\begin{Verbatim}[fontsize=\small]
  <cull faces="back" />
  <framebuffer>
    <attachment usage="color" link="coords-texture-1" />
    <use program="primary-coords-program">
      <uniform name="MVPMatrix" usage="modelviewprojection" />
      <instance of="cube-1-group" />
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="fourth-pass-program">
      <instance of="intersection-group" />
    </use>
  </framebuffer>
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <blend enabled="true" />
  <depth function="less" />
  <sort>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-1" />
        <use program="primary-coords-program">
          <cull faces="front" />
          <instance of="cube-1-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull faces="back" />
        <group id="cube-1-group">
          <translate x="-1">
            <cube id="cube-1" />
          </translate>
        </group>
      </use>
    </group>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-2" />
        <use program="primary-coords-program">
          <cull faces="front" />
          <instance of="cube-2-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull faces="back" />
        <group id="cube-2-group">
          <translate x="+1">
            <cube id="cube-2" />
          </translate>
        </group>
      </use>
    </group>
  </sort>
\end{Verbatim}
